<!-- R Commander Markdown Template -->

Replace with Main Title
=======================

### Ce PC

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

```{r}
Data <- readXL("C:/Users/Ce PC/Downloads/SDA.xlsx", rownames=FALSE, header=TRUE, na="", sheet="Feuil1", 
  stringsAsFactors=TRUE)
```


### Independent-Samples t-Test: expérience_agricole~sexe
```{r}
t.test(expérience_agricole~sexe, alternative='two.sided', conf.level=.95, var.equal=FALSE, data=Data)
```


### Histogram: expérience_agricole
```{r}
with(Data, Hist(expérience_agricole, groups=Age, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Histogram: expérience_agricole
```{r}
with(Data, Hist(expérience_agricole, groups=sexe, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Histogram: expérience_agricole
```{r}
with(Data, Hist(expérience_agricole, groups=Niveau.d..étude.., scale="percent", breaks="Sturges", col="darkgray"))
```


### Histogram: expérience_agricole
```{r}
with(Data, Hist(expérience_agricole, groups=Age, scale="percent", breaks="Sturges", col="darkgray"))
```


### Histogram: expérience_agricole
```{r}
with(Data, Hist(expérience_agricole, groups=sexe, scale="percent", breaks="Sturges", col="darkgray"))
```

```{r}
library(abind, pos=19)
```



### Two-Way Contingency Table: sexe, Niveau.d..étude..
```{r}
local({
  .Table <- xtabs(~sexe+Niveau.d..étude.., data=Data)
  cat("\nFrequency table:\n")
  print(.Table)
  .Test <- chisq.test(.Table, correct=FALSE)
  print(.Test)
})
```


### Frequencies: sexe
```{r}
local({
  .Table <- with(Data, table(sexe))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
  .Probs <- c(0.5,0.5) 
  chisq.test(.Table, p=.Probs)
})
```

```{r}
library(e1071, pos=20)
```



### Summarize Data Set: Data
```{r}
summary(Data)
```



### Frequencies: Age
```{r}
local({
  .Table <- with(Data, table(Age))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
  .Probs <- c(0.333333333333333,0.333333333333333,0.333333333333333) 
  chisq.test(.Table, p=.Probs)
})
```

```{r}
Datas <- readXL("C:/Users/Ce PC/Downloads/SDA.xlsx", rownames=FALSE, header=TRUE, na="", sheet="Feuil1", 
  stringsAsFactors=TRUE)
```


### Frequencies: Age
```{r}
local({
  .Table <- with(Datas, table(Age))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
  .Probs <- c(0.5,0.5) 
  chisq.test(.Table, p=.Probs)
})
```


### Frequencies: Niveau.d..étude..
```{r}
local({
  .Table <- with(Datas, table(Niveau.d..étude..))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
  .Probs <- c(0.25,0.25,0.25,0.25) 
  chisq.test(.Table, p=.Probs)
})
```


### Frequencies: Nom._.commune


### Frequencies: Type_agriculturep
```{r}
local({
  .Table <- with(Datas, table(Type_agriculturep))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
  .Probs <- c(0.5,0.5) 
  chisq.test(.Table, p=.Probs)
})
```


### Frequencies: Nom_viliage

```{r}
Datase <- readXL("C:/Users/Ce PC/Downloads/SDA.xlsx", rownames=FALSE, header=TRUE, na="", sheet="Feuil1", 
  stringsAsFactors=TRUE)
```


### Frequencies: Nom._.commune
```{r}
local({
  .Table <- with(Datase, table(Nom._.commune))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
})
```


### Frequencies: Nom._.commune
```{r}
local({
  .Table <- with(Datase, table(Nom._.commune))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
  .Probs <- c(0.142857142857143,0.142857142857143,0.142857142857143,0.142857142857143,0.142857142857143,
  0.142857142857143,0.142857142857143) 
  chisq.test(.Table, p=.Probs)
})
```


### Independent-Samples t-Test: expérience_agricole~sexe
```{r}
t.test(expérience_agricole~sexe, alternative='two.sided', conf.level=.95, var.equal=FALSE, data=Datase)
```


### Independent-Samples t-Test: expérience_agricole~Age
```{r}
t.test(expérience_agricole~Age, alternative='two.sided', conf.level=.95, var.equal=FALSE, data=Datase)
```

